---
title: "Replication_sample"
author: "Jacob Grippin"
date: "1/14/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
## Introdouction
```{r preparations, include=FALSE}
#Easier reference variable names in mtcars dataset
library(glue, lib.loc = "U:\\Documents\\Workshops Spring 2023\\Repro")
attach(mtcars)
#Store column names of dataset as a new object
names = colnames(mtcars)

changend <- table(vs)
#Help documentation for subset command
#?subset
vs0 <- subset(mtcars, vs == 0)
vs1 <- subset(mtcars, vs == 1)
#Help documentation for t.test command
#?t.test
testres <- t.test(vs0$mpg, vs1$mpg)
```

This is a short *memo*. Describing a dataset, showing some visuals. Put 2 spaces at end of line for output to go to next line.  

Load system dataset "mtcars". Column names of dataset included below.    
**`r colnames(mtcars)` **


### Variable Descriptions 
I am interested in variables for Miles Per Gallong(MPG) and VS. Their variable information is included below.  
Variable `r names[8]` has the following frequency counts.   
0         1  
`r changend`  

Variable `r names[1]` has the following measure of mean and standard deviation.  
**mean = **`r mean(mtcars$mpg)`  
**standard deviation **= `r sd(mtcars$mpg)`  

### Results
I am interested in the 'mpg' variable along with the 'vs' variable. I want to display mpg on a scatterplot and t-test results comparing mpg for vs values of 0 and 1. My null hypothesis would be the mpg for both vs groups are equal.  

```{r graph, echo=TRUE, include=TRUE, fig.height=6, fig.width=8, fig.cap="scatterplot mpg"}
plot(mtcars$wt, mtcars$mpg, ylab="mpg", xlab="weight", main = "Miles per Gallon of Cars by weight of cars in Sample")
```
As weight increased trend appears to result in decreased mpg. Below is correlation of mpg and weight relationship.  
`r cor(mtcars$mpg, mtcars$wt)`.  
  
Below are results of T-test mentioned earlier. My null hypothesis would be the mpg for both vs groups are equal.  
```{r ttest, include=TRUE, echo=TRUE}
#Commands below to compare avg mpg for vs equal to 0 and equal to 1. 
vs0 <- subset(mtcars, vs == 0)
vs1 <- subset(mtcars, vs == 1)
testres <- t.test(vs0$mpg, vs1$mpg)
#Print t.test results
testres
```
  
Above uses code chunk to show code used to create results. Also could do inline code just to show numbers. Numbers printed are *t statistic* and corresponding *p-value*. Indexing an object by its elements. Before I had referenced them by name. I could also reference by name if I wanted to by doing the following. `r c(testres$statistic, testres$p.value)`  

`r testres[c(1, 3)]`  

## Conclusion  
Based on such a low p-value I reject the null hypothesis. The data does not suggest that vs equal to 0 has the same mpg as vs equal to 1. vs equal to 1 has a much larger average mpg than vs equal to 0.  

Following links have good reference information:  
[Rmarkdown Webiste](https://rmarkdown.rstudio.com/) - tutorial rmarkdown  
[Rmarkdown cheatsheet](https://rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf) - cheatsheet 



